Train Harder, Smarter:\\Using Graph Theory to Create Route Suggestions

### 2013-12-04 paper.tex
Final commit before G's reading.

@@

Once the three prongs of this project have been integrated together, leveraging
the data from the other parts would also provide valuable input for the
algorithm. As mentioned in Section~\ref{sec:back}, cyclists generally perform
their own version of this algorithm to find routes that they will enjoy. Once
the web experience is fully fleshed out users will upload all of their rides
to the website so that they can be viewed and analyzed in the future. This also
provides extremely valuable data for the algorithm, since user generated routes
may favor better, more interesting roads than a purely weight driven experience.
With this data, the algorithm could add a ``heatmap'' layer to the algorithm
that keeps track of how popular a road is. Roads that are seldom used could be
weighted negatively, while extremely popular roads would be almost mandatorily
included in generated routes.

@@

>>>>

\begin{figure}
  \includegraphics[width=3in]{images/route.png}
  \caption{A Short Route in Troy} \label{img:route}
\end{figure}

Finally, consider the results that the loop generator produces. A sample route
is given in Figure~\ref{img:route}. This is a short loop with a distance goal of
one mile generated in eastern Troy. Unfortunately, some issues with the
algorithm remain, as there are far too many situations where the algorithm
creates a U-turn. That being said, it does do a decent job of generating a path
that covers nearby roads to travel along. Indeed, especially at the beginning of
the project, the routes don't need to be perfect. Instead, the vision involves
the user uitlizing the algorithm to generate a prototype for a route and
altering it slightly to avoid known bad roads or to take scenic detours, and
other minor adjustments.

@@

Once the three prongs of this project have been integrated together, leveraging
the data from the other parts would also provide valuable input for the
algorithm. As mentioned in Section~\ref{sec:back}, cyclists generally perform
their own version of this algorithm to find routes that they will enjoy. Once
the web experience is fully fleshed out users will upload all of their rides
to the website so that they can be viewed and analyzed in the future. This also
provides extremely valuable data for the algorithm, since user generated routes
may favor better, more interesting roads than a purely weight driven experience.
With this data, the algorithm could add a ``heatmap'' layer to the algorithm
that keeps track of how popular a road is. Roads that are seldom used could be
weighted negatively, while extremely popular roads would be almost mandatorily
included in generated routes. One interesting challenge to avoid here would be
dealing with population density. That is, there may be a rural road that is
everything a cyclist could desire, while city riding is absolutely nightmarish.
Unfortunately, the city also has a much higher population density, so even
riders riding in the city only to get out of it and find better roads will
likely add more ``heat'' to unpleasant city roads than to beautiful rural
roads.

@@

All of these pieces are hypothetical additional features to add; however, there
is room for improvement on the algorithm laid out here as well. Further
development on this algorithm should include a refinement of the weight
generation formulas, including experimentation with increasing adherence to the
ideal loop.
